Blockchain System

### 2021-01-04 papers/execution-model/model.tex

A \emph{pending operation} is represented by
$\langle  \OP, \TIME, \STATUSPENDING\rangle $,
where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected.
Once it is accepted, it changes to an \emph{accepted operation}:
$\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
$\TIME'> \TIME$ is the  when the operation was included in the
blockchain.  The operation can also be dropped at any time, which is
represented by
$\langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
causes for dropping, primarily timeout or overflow of the pending
pool which is limited in size in the implementation.

@@

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
\fi
Rule 1 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }
    \SystemTrans
    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    } \SystemTrans
    { [\EC{\RAISE\ \ERRBAL} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of public key]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \OP.\ADDR) \\
    % \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    } \SystemTrans
   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
     % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of fee]:\todo{Q: is this a local test? move to node transitions?}
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\PUK, \ADDR, \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    } \SystemTrans
    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
\iffalse 
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}
\fi
\subsection{Smart Contracts}
A. Originate
~\\
~\\
Rule 1 [injected]:

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
  }{
    [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of code]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPRG (\CODE, \STRING) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
     \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 5 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}

@@

    \NEG\ \CHECKPUB (\MANAGERS, \PUK) \
  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUK] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}

@@

    \NEG\ \CHECKPUB (\CONTRACTORS, \PUH) 
  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUH] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}

@@

    $n$ = \TIME\ - \TIME''

@@

    \NEG\ \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)
  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}

@@

    \item Function \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)\ checks whether an address  \ADDR\ exists in either \PENDING\ or \ACCEPTED.

>>>>

A \emph{pending operation} is represented by
$\langle  \OP, \TIME, \STATUSPENDING\rangle $,
where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected.
Once it is accepted, it changes to an \emph{accepted operation}:
$\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
$\TIME'> \TIME$ is  when the operation was included in the
blockchain.  The operation can also be dropped at any time, which is
represented by
$\langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
causes for dropping, primarily timeout or overflow of the pending
pool which is limited in size in the implementation.

@@

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
\fi
Rule 1 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }
    \SystemTrans
    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    } \SystemTrans
    { [\EC{\RAISE\ \ERRBAL} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of public key]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
    % \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    } \SystemTrans
   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
     % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of fee]:\todo{Q: is this a local test? move to node transitions?}
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\OP.\PUK, \OP.\PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    } \SystemTrans
    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
  }
\end{mathpar}
\iffalse 
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}
\fi
\subsection{Smart Contracts}
A. Originate
~\\
~\\
Rule 1 [injected]:

\begin{mathpar}
  \inferrule[Block-Originate]{
   \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
  }{
    [\EC\OP  :: \EXPRS, \ACCOUNTS,
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of code]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPRG (\CODE, \STRING) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
     \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 5 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}

@@

    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK) \
  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUK] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NEG\ \CHECKPUB (\BLOCKCHAIN.\CONTRACTORS, \PUH) 
  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUH] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    $n$ \ = \TIME\ - \TIME''

@@

    \NEG\ \CHECKEXIST (\OPH, \BLOCKCHAIN.\PENDING, \BLOCKCHAIN.\ACCEPTED)
    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \item Function \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)\ checks whether an operation  \OPH\ exists in either \PENDING\ or \ACCEPTED.
